Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/competing_bandits.tex
An edit in related work.

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system
    \cite{Frazier-ec14,Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    (see \cite{DynAuctions-survey10} for background),
pay-per-click auctions
    \cite{MechMAB-ec09,DevanurK09,Transform-ec10-jacm}
%\cite{Amin-auctions-nips13,Jieming-ec18},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.

>>>>

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system,
    \eg \cite{Kremer-JPE14,Frazier-ec14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    (see \cite{DynAuctions-survey10} for background),
online ad auctions, \eg
    \cite{MechMAB-ec09,DevanurK09,NSV08,Transform-ec10-jacm,Amin-auctions-nips13},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.
